\begin{frame}[t]{Definitions}
\begin{itemize}
\uncover<1->{\item The SAT Problem (\textbf{SAT}).}
\uncover<2->{\item Counting SAT Problem (\textbf{\#SAT}).}


\uncover<6->{\item Negation Normal Form (\textbf{NNF}).}
\uncover<7->{\item Conjunctive Normal Form (\textbf{CNF}).}
\uncover<8->{\item Decomposable Negation Normal Form (\textbf{DNNF}).}
\uncover<9->{\item deterministic Decomposable Negation Normal Form (\textbf{d-DNNF}).}
\uncover<10->{\item decision Decomposable Negation Normal Form (\textbf{dec-DNNF}).}
\end{itemize}

\only<1>{
\begin{block}{SAT}
\begin{itemize}
\item[--] Given a Boolean formula $\varphi$ of $n$ variables.
\item[?] Find an assignment that satisfies $\varphi$.
\end{itemize}
\end{block}
}

\only<2>{
\begin{block}{\#SAT}
\begin{itemize}
\item[--] Given a Boolean formula $\varphi$ of $n$ variables.
\item[?] How many assignments in $2^{\mathrm{Var}(\varphi)}$ satisfy $\varphi$?
\end{itemize}
\end{block}
}

\only<3-4>{
\begin{block}{Notation}
Let $\mathrm{SAT}(\chi) \subseteq 2^{\mathrm{VAR}(\chi)}$ be the set of all satisfying assignments of $\chi$
\vspace{-0.3cm}
$$\mathrm{SAT}(\chi) = \{\rho:\mathrm{VAR}(\chi) \rightarrow \{0, 1\} : \rho(\chi) = 1\}.$$
\vspace{-0.8cm}
\uncover<4->{$$\text{SAT: Is } \mathrm{SAT}(\varphi) = \emptyset.
\qquad \qquad \qquad
\text{\#SAT: Find } |\mathrm{SAT}(\varphi)|.$$}
\vspace{-0.6cm}
\end{block}
}

\only<5>{
\begin{block}{Example}
$$\varphi = X_1 \land (X_2 \lor \lnot X_3)$$
Clearly, \#SAT($\varphi$) = 3.
\end{block}
}

\only<6>{
\begin{block}{Negation Normal Form}
A Boolean formula $\varphi$ is in NNF form, if it contains only disjunctions and conjunctions over a set of positive and(or) negative literals.

\textbf{Example.} $\varphi = X_1 \lor \lnot X_2$.
\end{block}
}

\only<7>{
\begin{block}{Conjunctive Normal Form}
A Boolean formula $\varphi$ is in CNF, if it is a conjunction of one or more clauses, where each clauses is a disjunction of one or more literals. Note that each CNF formula is an NNF formula as well.
\end{block}
}

\only<8>{
\begin{block}{Decomposable Negation Normal Form}
A Boolean formula $\varphi$ is in DNNF, if it is in NNF and for each conjunction subformula $phi' := \psi_1 \land \psi_2$ we have $\mathrm{VAR}(\psi_1) \cap \mathrm{VAR}(\psi_2) = \emptyset$.
\end{block}
}

\only<9>{
\begin{block}{deterministic Decomposable Negation Normal Form}
A Boolean formula $\varphi$ is in d-DNNF, if it is in DNNF and for each disjunction subformula  $\varphi' = \psi_1 \lor \psi_2$ we have $\mathrm{SAT}(\psi_1) \cap \mathrm{SAT}(\psi_2) = \emptyset$.
\end{block}
}

\only<10->{
\begin{block}{decision Decomposable Negation Normal Form}
A Boolean formula $\varphi$ is in dec-DNNF, if it is in DNNF and each disjunction subformula  $\varphi'$ is of the form $\varphi' = (X \land \psi_1) \lor (\lnot X \land \psi_2)$ for some variable $X \in \mathrm{VAR}(\varphi)$.

\uncover<11>{\textbf{Note.} Each dec-DNNF is a d-DNNF.}
\end{block}
}
\end{frame}

\begin{frame}[t]{Assignments}
	\begin{itemize}[<+->]
		\item Given a CNF Formula $\varphi$, an \textbf{assignment} for $C$ is a function $\tau : \mathrm{VAR}(C) \rightarrow \{0, 1\}$.
		\item For $V' \subseteq \mathrm{VAR}(C)$, we define the \textbf{partial assignment} $\tau_{|V'} : V' \rightarrow \{0, 1\}$ as $\tau$ restricted to the variables in $V'$.
		\item A partial assignment $\tau_{|V'}$ satisfies a CNF-formula $\varphi$ ($\tau_{|V'} \models \varphi$), if for each clause $C \in \varphi$ there is a variable $v \in \mathrm{VAR}(C) \cap V'$ such that $\tau_{|V'}(v) = 1$ if and only if $v$ appears in $C$ as a positive literal.

	\end{itemize}
	\uncover<4>{
	\begin{block}{Example}
		$$\varphi := (v_1 \lor \lnot v_2 \lor v_3) \land (v_1 lor v_2) \land (\lnot v2 \lor \lnot v_3)$$
		For $V' = \{v_1, v_2\}, \tau_{|V'}(v_1) = 1, \tau_{|v'}(v_2) = 0$,
		the partial assignment $\tau_{|V'}$ satisfies $\varphi$.
	\end{block}
	}
\end{frame}


\begin{frame}[t]{Hypergraphs}
	\begin{minipage}{.59\linewidth}
	\begin{itemize}
		\item Hypergraph $\mathcal{H}$.
			\begin{itemize}
				\item A set of vertices $V(\mathcal{H})$.
				\item Edges $E(\mathcal{H})$, defined as 
				\item[] subsets over $V(\mathcal{H})$.
			\end{itemize}

		\uncover<2->{\item A walk is sequence $(e_1, x_1, \dots, x_n, e_{n+1})$, 
		\item[] $e_i \in \mathcal{H}, x_i \in V(\mathcal{H})$ and 
	\item[] $x_i \in e_{i} \cap e_{i-1}$ for all $i \in [n]$.}

		\uncover<3->{\item A \textbf{path} is a walk that never goes twice through the same vertex nor the same edge.}

		\uncover<4->{\item Different ways to translate
		\item[] \hspace{1cm} acyclicity to  hypergraphs.}

	\end{itemize}
\end{minipage}
\begin{minipage}{.39\linewidth}
\centering
\input{figures/hypergraph.tex}
\end{minipage}
\footnotetext[1]{$e_{|\geq i} := e \cap \{v_i, \dots v_n\}$.}
\end{frame}

\begin{frame}[t]{$\beta$-acyclic graphs}
	\begin{itemize}
		\item Let $\rho := v_1, \dots v_n$ be an enumeration of the vertices.
		\uncover<2->{\item $\rho$ is a $\beta$-elimination, if for all}
		\uncover<3->{\item[] \hspace{1cm}$e_1, e_2 \in E(\mathcal{H})$ and $v_i \in e_1 \cap e_2$,
		\item[]\hspace{1cm}$e_{1|\geq i} \subseteq e_2$ or $e_{2|\geq i} \subseteq e_1$.}
		\uncover<4->{\item A hypergraph is $\beta$-acyclic, if it admits a $\beta$-elimination.}
		\uncover<5->{\item We define $V_{\leq v_i} := \{v_j ; j\leq i\}$.}

	\end{itemize}

	\begin{center}
		\input{figures/hypergraph.tex}
	\end{center}

\end{frame}

	

